Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-01-12 ForegroundSimulations/ms.tex
Add figures to git, reorganize section headings
From 689699b (master):
=====================

Add .eps figures to git repo

In ms.tex,

(*) Reorganize section and subsection headings

\shorttitle{Estimate of Foregrounds in EoR Power Spectra for HERA}
\shortauthors{Thyagarajan et~al.}

@@

\title{Estimation of Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra with the Hydrogen Epoch of Reionization Array}

@@

@@

\section{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}

@@

\subsection{The Hydrogen Epoch of Reionization Array}\label{sec:HERA}

\subsubsection{Antenna Power Pattern}

@@

\subsubsection{Antenna Reflectometry}

@@

\section{Analysis of Foreground Signatures}\label{sec:FG-analysis}

>>>>

\shorttitle{Characterization of Beam Chromaticity in EoR Power Spectra Measurements}
\shortauthors{Thyagarajan et~al.}

@@

\title{Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra}

@@

\section{The Hydrogen Epoch of Reionization Array}\label{sec:HERA}

@@

\subsection{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}

@@

\subsection{Antenna Power Pattern}

@@

\section{Chromaticity of Power Pattern}

\subsection{Directional Chromaticity}

\subsection{Effect on Delay Power Spectrum}

\subsection{Constraints on Antenna-to-Antenna Reflections}

@@
